---
title: "Untitled"
format: html
editor: visual
---

## Functions

Make a function that doubles a value.

```{r}
double_value <- function(my_dollars) {
  print(2 * my_dollars)
}
```

```{r}
double_value(my_dollars = 10.13)
```

```{r}
monthly_income <- c(42, 50, 61, 75, 89, 50)

double_value(monthly_income)
```

Create a function that returns an awesome restaurant name given an cool animal and your favorite food.

```{r}
name_restaurant <- function(animal, food) {
  print(paste0(animal, food))
}

name_restaurant(animal = "hawk", food = "pizza")
```

Given temperature in degrees fahrenheit, write a function that converts it to Celsius.

#(32**°F** − 32) × 5/9 = 0**°C**

|     |
|-----|
|     |

```{r}

convertFtoC <- function(temp_f) {
  print((temp_f -32) * (5/9))
}
```

```{r}
convertFtoC(temp_f = 52)
```

Create a function that given inputs of age and hometown, returns "I am \_\_ years old, and I'm from \_\_\_."

```{r}
age_hometown <- function(age, hometown) {
  print(paste("I am", age, "years old, and I'm from", hometown))
}

age_hometown(age= 6, hometown = "Los Angeles")
```

# Functions with conditionals

```{r}
calculate_animal_age <- function(species, age_human_years) {
  if(species == "dog") {
    age_human_years * 7
  } else if (species == "goat") {
    age_human_years * 4.7
  } else {
    print("Please enter dog or goat.")
  }
}
```

```{r}
calculate_animal_age(species = "dog", age_human_years = 10)

calculate_animal_age(species = "whale", age_human_years = 4)
```

Write a function that, given temperature in Kelvin, if a user selects "metric" to the scale then return degrees Celsius, or if they select "english" then return degrees in Fahrenheit.
